The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-06-12 albatros_paper.tex
HCC small fixes

The primary requirements that drive the design for a low-frequency
imaging experiment are 1) desired resolution, 2) low RFI, and 3) quiet
ionospheric conditions.  As a benchmark, an interferometer operating
at 30~MHz requires baseline lengths of $\sim 0.5-1$~km 
to achieve a resolution of $\sim 1$\degree.  This length scales
inversely with frequency, and therefore $\sim 10$-km lengths are
required at few-MHz frequencies to improve substantially upon the resolutions
achieved to date.  The experiment installation site must be remote to
keep RFI to a minimum.  , and polar or near-polar latitiudes generally
have lower ionospheric plasma frequency cutoffs relative to other
locations on Earth.  \autoref{Fig:iri} illustrates predictions from
the International Reference Ionosphere
model~\citep{2018AdRS...16....1B} for the minimum plasma frequency
during the last solar minimum, which started in approximately 2007.
Three locations are shown: Marion Island, the focus of this work;
Dome~C in Antarctica, which is another isolated location used for
astronomical observations; and Hobart, Tasmania, where Reber performed
his $\sim2$~MHz observations.  The model predictions illustrate that
the ionospheric plasma cutoff frequency at Marion Island may drop as
low as $\sim1.5$~MHz during solar minima.  Since we are currently
experiencing another solar minimum~\citep{2018NatCo...9.5209B}, the
timing is opportune for new low-frequency observations.

>>>>

The primary requirements that drive the design for a low-frequency
imaging experiment are 1) desired resolution, 2) low RFI, and 3) quiet
ionospheric conditions.  As a benchmark, an interferometer operating
at 30~MHz requires baseline lengths of $\sim0.5$--1~km 
to achieve a resolution of $\sim 1$\degree.  This length scales
inversely with frequency, and therefore $\sim 10$-km lengths are
required at few-MHz frequencies to improve substantially upon the resolutions
achieved to date.  The experiment installation site must be remote to
keep RFI to a minimum, and polar or near-polar latitiudes generally
have lower ionospheric plasma frequency cutoffs relative to other
locations on Earth.  \autoref{Fig:iri} illustrates predictions from
the International Reference Ionosphere
model~\citep{2018AdRS...16....1B} for the minimum plasma frequency
during the last solar minimum, which started in approximately 2007.
Three locations are shown: Marion Island, the focus of this work;
Dome~C in Antarctica, which is another isolated location used for
astronomical observations; and Hobart, Tasmania, where Reber performed
his $\sim2$~MHz observations.  The model predictions illustrate that
the ionospheric plasma cutoff frequency at Marion Island may drop as
low as $\sim1.5$~MHz during solar minima.  Since we are currently
experiencing another solar minimum~\citep{2018NatCo...9.5209B}, the
timing is opportune for new low-frequency observations.
